### 2017-01-02 paper/evaluation.tex
updated listing and explanation

To evaluate the frequency of time-consuming regression tests, we
considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our scripts
to test each subject. The main loop (line 12) iterates over the list
of subjects and invokes the wrapper function \emph{run} to execute
Maven in separated steps (lines 14-16). To avoid inflating the
measured time, we first compile the source and test files (line 14),
fetch all dependencies (line 15) and later, we run the tests in offline
mode (line 16) to avoid package updates. In addition we randomly
selected 100 Maven logs to inspect and identify non-related tasks
(\eg, \emph{javadoc} generation and static analysis). We created a
list of plugins (lines 1-5) to ignore them during the test execution.
Finally, we use a simple regular expression over the test output to
extract the elapsed time.

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
}
\begin{lstlisting}[language=Python]
MAVEN_IGNORES = [
   "-Drat.skip=true", "-Dmaven.javadoc.skip=true",
   "-Djacoco.skip=true", "-Dcheckstyle.skip=true",
   "-Dfindbugs=true", "-Dcobertura.skip=true"
]

def run(cmds, opts=None):
   if opts not None:
      cmds.extend(opts)
   subprocess.call(cmds)

for subject in SUBJECTS:
   os.chdir(subject)
   run(["mvn", "clean", "install", "-DskipTests"])
   run(["mvn", "dependency:go-offline"])
   run(["mvn", "-o", "test"], MAVEN_IGNORES)
\end{lstlisting}
\caption{\label{fig:mvn-execution} Python script to evaluate the time cost of
    test suites. For each subject, we compile the source and test files, fetch
    all dependencies, and execute the tests in offline mode ignoring
    non-related tasks.}
\end{figure}

>>>>

To evaluate the frequency of time-consuming regression tests, we
considered the \SubjCnt{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 6-12) iterates over the
list of subjects and invokes Maven in separated steps (lines 8-10). To
avoid inflating the measured time, we first compile the source and
test files (line 8), fetch all dependencies (line 9) and later, we
run the tests in offline mode (line 10) to avoid package updates. In
addition we randomly selected 100 Maven logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static
analysis). We created a list of plugins (lines 1-4) to ignore them
during the test execution.  Finally, we use a simple regular
expression over the test output to extract the elapsed time (line 13).

\begin{figure}[h!]
\centering
\scriptsize
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}[language=Bash]
MAVEN_IGNORES="-Dmaven.javadoc.skip=true \
    -Drat.skip=true -Djacoco.skip=true \
    -Dcheckstyle.skip=true -Dfindbugs=true \
    -Dcobertura.skip=true"

for subj in ${SUBJECTS}; do
    cd ${SUBJECTS_HOME}/${subj}
    mvn clean install -DskipTests ${MAVEN_IGNORES}
    mvn dependency:go-offline
    mvn -o test ${MAVEN_IGNORES} &> ${LOG}
    cat ${LOG} | grep "\[INFO\] Total time:"
done
\end{lstlisting}
\caption{\label{fig:mvn-execution} Bash script to evaluate the time cost of
    test suites. For each subject, we compile the source and test files, fetch
    all dependencies, and execute the tests in offline mode ignoring
    non-related tasks. Unnecessary commands are omitted for simplicity.}
\end{figure}
